Technical Report

### 2018-05-24 fully-abstract-comp/ftlr-proof-cases.tex
added some labels, fixed reference.

  \item $\Phi_S \step[\gc] \halted$ and $\Phi_T \step\halted$

@@

  \item All of the following hold:

@@

In case \ref{case:ftlr:failed}, both executions go to failed. In this case, we
either assume that the target configuration terminates or that the source
configuration terminates, but in either case it leads to a contradiction with
the failing configuration.

In case \ref{case:ftlr:get-and-arith-op}, we use the induction hypothesis to get
\[
  \npair[n'-1]{(((\perm,\lin),\baddr,\eaddr,\aaddr+1),((\perm,\lin),\baddr,\eaddr,\aaddr+1))} \in \lre(W)
\]
This is possible by using the initial assumptions along with Lemma \ref{lem:downwards-closed}.
By Lemma~\ref{lem:downwards-closed}, we know $\memSat[n'-1]{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$.
By Lemma~\ref{lem:downwards-closed} and the fact that integers are always safe,
we know $\npair[n'-1]{(\reg_S\update{r}{z},\reg_T\update{r}{z})} \in \lrr(W_R)$.
This allows us to conclude
\[
  \npair[n'-1]{(\Phi_S',\Phi_T')} \in \lro
\]
as desired.

>>>>

  \item \label{case:ftlr:halted} $\Phi_S \step[\gc] \halted$ and $\Phi_T \step\halted$

@@

  \item \label{case:ftlr:call} All of the following hold:

@@

In case \ref{case:ftlr:failed}, both executions go to failed. In this case, we
either assume that the target configuration terminates or that the source
configuration terminates, but in either case it leads to a contradiction with
the failing configuration.
\\\\
In case \ref{case:ftlr:halted}, both source and target configuration halts in 0
steps, so both directions of $\lro$ are trivially satisfied.
\\\\
In case \ref{case:ftlr:get-and-arith-op}, we use the induction hypothesis to get
\[
  \npair[n'-1]{(((\perm,\lin),\baddr,\eaddr,\aaddr+1),((\perm,\lin),\baddr,\eaddr,\aaddr+1))} \in \lre(W)
\]
This is possible by using the initial assumptions along with Lemma \ref{lem:downwards-closed}.
By Lemma~\ref{lem:downwards-closed}, we know $\memSat[n'-1]{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$.
By Lemma~\ref{lem:downwards-closed} and the fact that integers are always safe,
we know $\npair[n'-1]{(\reg_S\update{r}{z},\reg_T\update{r}{z})} \in \lrr(W_R)$.
This allows us to conclude
\[
  \npair[n'-1]{(\Phi_S',\Phi_T')} \in \lro
\]
as desired.

### 2018-05-24 fully-abstract-comp/technical-report.tex
added some labels, fixed reference.

     This follows by induction and Lemma~\ref{lem:non-expansive} (if $\vsc \not\in \overline{c_{\mathrm{import}}}$) or by assumption (if $\vsc \in \overline{c_{\mathrm{import}}}$), we know that $\npair[n']{(\vsc,\vsc)} \in \lrv(W)$.

>>>>

     This follows by induction and Lemma~\ref{lem:downwards-closed} (if $\vsc \not\in \overline{c_{\mathrm{import}}}$) or by assumption (if $\vsc \in \overline{c_{\mathrm{import}}}$), we know that $\npair[n']{(\vsc,\vsc)} \in \lrv(W)$.
